                %-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://buffalo.edu/~tuckerpo}{\Large Tucker J. Polomik}} & GitHub: \href{https://github.com/tuckerpo}{https://github.com/tuckerpo}\\
  Email: \href{mailto:tuckerpo@buffalo.edu}{tuckerpo@buffalo.edu} & LinkedIn: \href{https://linkedin.com/in/tuckerpo}{https://linkedin.com/in/tuckerpo}\\
  Phone: (845) 381-8007 & Personal Site: \href{http://buffalo.edu/~tuckerpo}{http://buffalo.edu/$\sim$tuckerpo}
 
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University at Buffalo, School of Engineering}{Buffalo, NY}
      {Bachelor of Science in Computer Engineering}{Expected Sept. 1, 2018}
  \resumeSubHeadingListEnd
  
  %-----------PROJECTS-----------------
  \section{Personal Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{InMoov Robotics Simulation}
  {Worked on a team of 6 to create a bipedal motion simulator for an open-source CAD tool called "Choreonoid". Wrote C++ code that models bipedal kinematics and Python scripts that automate animations. Followed the agile software development pattern with bi-weekly sprints.} \vspace{1.5mm}
  \resumeSubItem{Carduino (Autonomous RC vehicle)}
  {Write C code on an ATmega328P chip that controls servos and motors on an RC vehicle. Concurrently parse data from an ultrasonic sensor to calculate the vehicle's distance to things around it, changing the angle of the servos to avoid collisions accordingly. }\vspace{1.5mm}
  \resumeSubItem{I'm Hungry}
  {Full-stack developer for a Node.js Yelp clone. Integrated back-end and database MySQL functionality with AWS. Wrote registration, log-in, and session storing modules; regularly back-up database. }\vspace{1.5mm}
  \resumeSubItem{RTCV}{Platform-independent real-time computer vision project. Accesses a system's webcam and allows the user to apply various image filters and segmentations in real-time with minimal FPS loss. Written in Python.}
  \iffalse
  \resumeSubItem{CppNews}{Used the Twitter open API with Python library Tweepy to make a data-scraping bot. Retweets things related to the C++ language if it's deemed popular by internal API data (number of likes relative to followers, follower engagement, etc).}
  \fi
  \resumeSubHeadingListEnd
  


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
  
  \resumeSubheading
  {KGB AVIATION SOLUTIONS, LLC.}{West Seneca, NY}
  {\textbf{Capstone Project}}{February 2018 - May 2018}
  \resumeItemListStart

   \resumeItem{FDR Interfacing Tool}{Worked with the company CEO and several other interns to build an interfacing system for flight data recorders (FDRs). }
  \resumeItem{Reverse Engineering}
  {Determined the proprietary handshaking protocol \& RS-422 signal timing patterns of FDRs. }

   \resumeItem{Analog Tooling}{Used a Tek oscilloscope and Digilent bus analyzer to determine character encoding, start-stop, parity and baud rate of serial streams.}
    
  \resumeItem{Data Download}{Wrote a Python script which pulls data from the FDR and stores it to removable, non-volatile flash memory.}
  \resumeItem{Shipped Product}{Managed to take an idea from the planning stages and progress to a tangible, secure, shippable embedded system in four months time.}
 
  \resumeItemListEnd

\resumeSubheading{University at Buffalo}{Buffalo, NY}{ \textbf{Digital Teaching Assistant CSE421/521 - Operating Systems}}{September 2018 - Present}
	\resumeItemListStart
		\resumeItem{Student Inquiries}{Answer student questions through the Piazza platform and over email. Provide systems level  and C programming help.}
		\resumeItem{Material Correspondence}{Typeset the University at Buffalo student programming guide for the Stanford operating system \textit{PintOS} in Latex. }
	\resumeSubHeadingListEnd

	\resumeSubheading
	{WNY Food Web}{Buffalo, NY}
	{\textbf{Volunteer Software Developer}}{June 2017 - July 2017}
	\resumeItemListStart
	\resumeItem{Poverty Relief}
	{Wrote code to interact with user and database in Typescript \& SQL. }
	\resumeItemListEnd
	

       \resumeSubheading
      {Hannaford Bros Supermarket}{Pine Bush, NY}
      {\textbf{Customer Service Clerk}}{March 2014 - September 2015}
      \resumeItemListStart
      \resumeItem{Customer Service}
     {Encouraged continued patronage in a small-town environment. Performed store maintenance. Worked in tandem with new hires to familiarize them with job duties.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{:Java, C++, C, JavaScript, Python, SQL, ARM} }
     \hfill
     \item{
      \textbf{Tools \& IDEs}{: Git, Eclipse, Visual Studio, \LaTeX, make, JUnit, vim, MySQL
   } 
\item{
	\textbf{OS/Platforms}{: Linux (armbian, Ubuntu), Windows, Android} }
	
} 
 \resumeSubHeadingListEnd
 
 %---------HARDWARE------------
 %\section{Hardware Skills}
 %\resumeSubHeadingListStart
 %\item{
% 	\textbf{HDLs/Software}{: Verilog, VHDL, Excel } }
% \hfill
% \item{
% 	\textbf{Laboratory Tools}{: Multi-trace Oscilloscope, Function Generators, DC PSU, Digital Multimeter }
 	% \hfill
 	%\item{
 %		\textbf{Relevant EE Coursework}{: Circuit Analysis, Signals and Systems, Electronic Devices/ICs \& Electronic Devices/ICs Lab  }
 %} 
%}
% \resumeSubHeadingListEnd
 
 
 
 


%-------------------------------------------
\end{document}